\section{Presentation Logic Layer}

%What pages will be present in your project? briefly indicate how your web site will be organized

Lyrify+ has two main areas: the user area and the artist area. Both are accessible through the login page where the user can decide to login as an user or as an artist, according to their role. The accessible pages for users can only be seen by users, idem for the artist, the only common page for both type of users is the login page.
Now we define the pages to be developed in Lyrify+.
\begin{itemize}
    \item Login / Register page: first shown page to all users. They will be able to choose to login as an user/artist or to register as a new user/artist.
    \item Homepage: main page showed when a user's is logged in.
    \item User profile page: page that shows the user personal data and account options.
    \item Artist profile page: page that shows the artist's personal data, upload options and account options.
    \item Artist page: page that shows the public data of an artist, including biography, songs and albums.
    \item Upload song page: page where it's possible to upload songs, only accessible by verified artists.
    \item Upload album page: page were it's possible to upload albums, only accessible by verified artists.
    \item Library page: page showing users' playlists, liked songs and added albums.
    \item Song page: page that shows information about the song.
    \item Playlist/Album page: page that shows information about the playlist or the album.
\end{itemize}


%For the main pages put a mockup and describe it in detail.

\input{sections/PLL/LoginPageInterfaceMockup}

\input{sections/PLL/HomePageInterfaceMockup}

\input{sections/PLL/ProfileUserInterfaceMockup}

\input{sections/PLL/ProfileArtistInterfaceMockup}

\input{sections/PLL/ArtistPageInterfaceMockup}

\newpage
\input{sections/PLL/UploadSongPageInterfaceMockup}

\input{sections/PLL/UploadAlbumPageInterfaceMockup}

\input{sections/PLL/LibraryPageInterfaceMockup}

\input{sections/PLL/SongPageInterfaceMockup}

\input{sections/PLL/PlaylistPageInterfaceMockup}
